On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-10-10 paper2.tex
changed title in Appendix A
dereddened text

\begin{figure*} 
\centering
\includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows the
  RLF of our extended CR model (see main text for the details of the chosen
  parameters) for different fractions of radio-loud clusters. Additionally shown
  is the contribution of radio-quiet and radio-loud populations to the total RLF
  (assuming a fraction of 25 per cent and 1 per cent of radio-loud objects). The
  top right panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z =
  0.2$, using our phenomenological gas model for $L_{\rmn{X,bol}}$ of each
  cluster; again for different percentages of radio-loud clusters.  The bottom
  left panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z
  = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for
  each cluster. The bottom right panel shows the comparison between the three
  approaches for 10 per cent of radio-loud clusters. In all panels, we show the NVSS
  survey RLF \citep{1999NewA....4..141G} with a median redshift of $z\approx
  0.18$, corrected for the sample incompleteness and survey sky coverage.
  Horizontal error bars represent the mass bins while the vertical error bars
  are Poissonian uncertainties. The light gray line marked by the arrow
  estimates the incompleteness limit owing to the adopted low-mass cut (in the
  construction of the mock cluster catalog, see Paper~I) and the scatter in the
  halo luminosities.}
\label{fig:RLF_1.4}
\end{figure*}

@@

In Fig.~\ref{fig:RLF_1.4}, we show the RH luminosity function (RLF) at 1.4~GHz
for a representative realization of our extended CR model (as in
Section~\ref{sec:4}), and compare it with observational results.  The RLF is
completely determined by the cluster mass function and the radio
luminosity-to-mass relation, through $L_{1.4~\rmn{GHz}}-L_{ \rmn{X,bol}}$ or
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ in combination with our phenomenological gas
model (see Paper~I). However, in the radio band there is the additional
uncertainty of the fraction of radio-loud clusters. Thus, in
Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the
\qc{observed} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
relations \qc{(as in Fig.~\ref{fig:PLSZ})} to our $z = 0.2$ mock catalog, which employs our phenomenological gas
model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster,
respectively. Note that this procedure is {\em only} applied to halos defined as
radio-loud clusters (which are by definition accounted for in the
$L_{1.4~\rmn{GHz}}$ scaling relations) and we assume a fraction of 1, 0.25, 0.1,
0.05 and 0.01 of radio-loud clusters. As evident from Fig.~\ref{fig:RLF_1.4},
this differs for our model scaling relations: there we also define a fraction of
radio-loud clusters, but the radio-quiet population also contributes to the RLF
with an increasing fraction at low luminosities. This is exemplified in the top
left plot of Fig.~\ref{fig:RLF_1.4}, which shows the contribution of radio-quiet
and loud populations to the total RLF, assuming a fraction of 0.25 and 0.01 of
radio-loud objects.

@@

\section{Cosmic Ray Modeling Details}
\label{app:B}

>>>>

\begin{figure*} 
\centering
\includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows the
  RLF of our extended CR model (see main text for the details of the chosen
  parameters) for different fractions of radio-loud clusters. Additionally shown
  is the contribution of radio-quiet and radio-loud populations to the total RLF
  (assuming a fraction of 25 per cent and 1 per cent of radio-loud objects). The
  top right panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see Fig.~\ref{fig:PLSZ})}
  to the MultiDark clusters at $z = 0.2$, using our phenomenological gas model
  for $L_{\rmn{X,bol}}$ of each cluster; again for different percentages of
  radio-loud clusters.  The bottom left panel shows the RLF obtained by applying
  the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation {\bf (see
    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using
  $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for each
  cluster. The bottom right panel shows the comparison between the three
  approaches for 10 per cent of radio-loud clusters. In all panels, we show the
  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of
  $z\approx 0.18$, corrected for the sample incompleteness and survey sky
  coverage.  Horizontal error bars represent the mass bins while the vertical
  error bars are Poissonian uncertainties. The light gray line marked by the
  arrow estimates the incompleteness limit owing to the adopted low-mass cut (in
  the construction of the mock cluster catalog, see Paper~I) and the scatter in
  the halo luminosities.}
\label{fig:RLF_1.4}
\end{figure*}

@@

In Fig.~\ref{fig:RLF_1.4}, we show the RH luminosity function (RLF) at 1.4~GHz
for a representative realization of our extended CR model (as in
Section~\ref{sec:4}), and compare it with observational results.  The RLF is
completely determined by the cluster mass function and the radio
luminosity-to-mass relation, through $L_{1.4~\rmn{GHz}}-L_{ \rmn{X,bol}}$ or
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ in combination with our phenomenological gas
model (see Paper~I). However, in the radio band there is the additional
uncertainty of the fraction of radio-loud clusters. Thus, in
Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the observed
$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
relations {\bf (as in Fig.~\ref{fig:PLSZ})} to our $z = 0.2$ mock catalog, which
employs our phenomenological gas model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ},
  500}$ of each cluster, respectively. Note that this procedure is {\em only}
applied to halos defined as radio-loud clusters (which are by definition
accounted for in the $L_{1.4~\rmn{GHz}}$ scaling relations) and we assume a
fraction of 1, 0.25, 0.1, 0.05 and 0.01 of radio-loud clusters. As evident from
Fig.~\ref{fig:RLF_1.4}, this differs for our model scaling relations: there we
also define a fraction of radio-loud clusters, but the radio-quiet population
also contributes to the RLF with an increasing fraction at low
luminosities. This is exemplified in the top left plot of
Fig.~\ref{fig:RLF_1.4}, which shows the contribution of radio-quiet and loud
populations to the total RLF, assuming a fraction of 0.25 and 0.01 of radio-loud
objects.

@@

\section{Cosmic Ray Modeling}
\label{app:B}
